---
title: "Serena's Group Assignment Code"
format:
  html:
    toc: true
    df-print: kable
    code-tools: true
    embed-resources: true
---

```{r, echo=FALSE} 

knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

```


```{r}
library(tidyverse)
library(haven)
library(srvyr)
library(survey)
library(gt)
library(forcats)

ess<- read_dta(unz("../Data/ESS11.zip", "ESS11.dta"))|>
  zap_missing()

# country = cntry, region = region, domicile = domicil, weight = anweight
# attachment to Europe = atcherp,vattachment to country = atchctr
# education years = eduyrs
# stay in EU = vteurmmb, join EU = vteubcmb, European unification = euftf
# psppsgva Political system allows people to have a say in what government does

```
           

## Q1
Are European people more emotionally attached “Europe” or to their individual countries of residence?
```{r}
svyess <- ess|>
  as_survey_design(
    ids = psu,
    strata= stratum,
    weight= anweight,
    nest=T)|>
  mutate(difference = atchctr-atcherp)

as.numeric(svymean(~difference, svyess, na.rm = TRUE))
```
People are more emotionally attached to their country. On average, people rate their attachment to their country 1.62 points higher than their country on a 10 point scale of attachment.


## Q2
How does this vary across countries or regions?
```{r}

by_country <- svyess|>
  select(cntry, difference)|>
  drop_na()|>
  group_by(cntry)|>
  summarize(mean= survey_mean(difference))
  
ggplot(by_country, aes(x=reorder(cntry, mean), y=mean))+
  geom_col(fill= "red2", color = "red4") +
  theme_minimal() +
  labs(title = "How much more do people feel attached to their country over Europe?",
       subtitle = "(mean attachment to country - mean attachment to Europe, scale from 1-10)",
       x = "\ncountry",
       y = "mean difference per country \n "
       )+
  theme(plot.title = element_text(face= "bold", hjust = 0.5), 
        plot.subtitle = element_text(hjust = 0.5))

```

By country, Israel has the strongest attachment to their country over Europe. Belgium has the weakest attachment to their country over Europe, though the difference is still positive. This means for every country, on average people are more attached to their country over Europe as a whole.

## Q3

What individual level characteristics are associated with stronger emotional attachments to one or the other?

```{r}
outliers <- boxplot.stats(ess$eduyrs)$out

# education -> country
by_educationC <- svyess|>
  select(eduyrs, atchctr)|>
  drop_na()|>
  group_by(eduyrs)|>
  summarize(mean= survey_mean(atchctr))

## Remove outliers
by_educationC <- by_educationC[!by_educationC$eduyrs %in% outliers, ]
  
ggplot(by_educationC, aes(x=eduyrs, y=mean))+
  geom_point(color = "blue3", size=3) +
  theme_minimal() +
  labs(title = "Education on attachment; home country",
       subtitle = "(mean attachment to home country, scale from 1-10)",
       x = "\nyears of education",
       y = "mean attachment to home country\n "
       )+
  theme(plot.title = element_text(face= "bold", hjust = 0.5), 
        plot.subtitle = element_text(hjust = 0.5))
# education -> Europe

by_education <- svyess|>
  select(eduyrs, atcherp)|>
  drop_na()|>
  group_by(eduyrs)|>
  summarize(mean= survey_mean(atcherp))

## Remove outliers
by_education <- by_education[!by_education$eduyrs %in% outliers, ]
  
ggplot(by_education, aes(x=eduyrs, y=mean))+
  geom_point(color = "blue3", size=3) +
  theme_minimal() +
  labs(title = "Education on attachment, Europe",
       subtitle = "(mean attachment to Europe, scale from 1-10)",
       x = "\nyears of education",
       y = "mean attachment to Europe\n "
       )+
  theme(plot.title = element_text(face= "bold", hjust = 0.5), 
        plot.subtitle = element_text(hjust = 0.5))

```
After removing outliers, there is a very clear relationship between years of education and attachment. As years of education increase, attachment to Europe increases and attachment to one's home country decreases.


## Q4

How do these attitudes also relate to attitudes towards the European union?

```{r}
eu_countries <- c("AT", "BE", "BG", "HR", "CY", "CZ", "DK", "EE", "FI", "FR", "DE", "GR", "HU", "IE", "IT", "LV", "LT", "LU", "MT", "NL", "PL", "PT", "RO", "SK", "SI", "ES", "SE")

svyess <- svyess|>
  mutate(is_eu = cntry %in% eu_countries)|>
  mutate(EU_opinion =
    case_when(
      ess$vteurmmb %in% 1 ~ "Stay in EU",
      ess$vteurmmb %in% 2 ~ "Leave EU",
      ess$vteubcmb %in% 1 ~ "Join EU",
      ess$vteubcmb %in% 2 ~ "Don't Join EU"))


EU_attitudes <- svyess|>
  select(difference, is_eu, EU_opinion)|>
  drop_na()|>
  group_by(is_eu, EU_opinion)|>
  summarize(mean = survey_mean(difference))|>
  ungroup()

EU_attitudes$is_eu <-
  factor(EU_attitudes$is_eu,
         labels = c("Not in EU", "EU Member"))

ggplot(EU_attitudes, aes(x=EU_opinion, y=mean, fill=EU_opinion))+
  geom_col() +
  scale_fill_manual(values = c("red3", "green3", "red3", "green3"))+
  theme_minimal() +
  labs(title = "Opinion on being in the EU on attachement to home country over Europe",
       subtitle = "(mean attachment to country - mean attachment to Europe, scale from 1-10)",
       x = "\nopinion on the EU",
       y = "mean difference per country \n "
       )+
  facet_wrap(~is_eu, ncol=2, scales='free_x') +
  theme(plot.title = element_text(face= "bold", hjust = 0.5), 
        plot.subtitle = element_text(hjust = 0.5),
        strip.text = element_text(face = "bold"),
        legend.position = "none")

```

On average, people who do not wish to be in the EU (whether that means not joining the union or leaving the union if they are a current member) feel a much stronger attachment to their country over those who wish to be in the EU. This is logical, since if they feel less attached to Europe in general they likely do not want to join union of European countries. An interesting data point is that there is slightly stronger attachment to their home country among EU members who want to stay over non-EU members who want to join, which could be because if someone wants to join the EU they may be disillusioned with the politics of their home country and feel less attached to it. 

## Q5 

Are people in EU member countries more or less likely to hold strong national attachments?
```{r}
svyess <- svyess|>
  mutate(is_eu = cntry %in% eu_countries)

by_country_EU <- svyess|>
  select(cntry, difference, is_eu)|>
  drop_na()|>
  group_by(cntry, is_eu)|>
  summarize(mean = survey_mean(difference))

by_country_EU$is_eu <-
  factor(by_country_EU$is_eu,
         labels = c("Not in EU", "EU Member"))
  
ggplot(by_country_EU, aes(x=reorder(cntry, mean), y=mean, fill=is_eu))+
  geom_col() +
  scale_fill_manual(values = c("red3", "goldenrod1"))+
  theme_minimal() +
  labs(title = "How much more do people feel attached to their country over Europe?",
       subtitle = "(mean attachment to country - mean attachment to Europe, scale from 1-10)",
       x = "\ncountry",
       y = "mean difference per country \n "
       )+
  facet_wrap(~is_eu, ncol=2, scales='free_x') +
  theme(plot.title = element_text(face= "bold", hjust = 0.5), 
        plot.subtitle = element_text(hjust = 0.5),
        strip.text = element_text(face = "bold"),
        legend.position = "none")

by_country_EU|>
  group_by(is_eu)|>
  summarize(mean_difference = mean(mean))|>
  slice_head(n=2)

```
Countries not in the EU have stronger attachment to their country than Europe than do countries in the EU. On average, the countries not in the EU rate their attachment to their country 2.69 points higher than Europe while countries in the EU rate their ties to their country only 1.77 higher than Europe. 

## Q6

Are there other aspects of people’s region of residence that correlate with national attachments?

```{r}

# political inclusiveness

by_inclusivity <- svyess|>
  select(psppsgva, difference, atcherp, atchctr)|>
  drop_na()|>
  group_by(psppsgva)|>
  summarize(mean=survey_mean(difference))

by_inclusivity$psppsgva <-
  factor(by_inclusivity$psppsgva,
         labels = c("Not at all", "Very Little", "Some", "A lot", "A great deal"))

ggplot(by_inclusivity, aes(x= psppsgva, y=mean)) +
  geom_col(fill = "pink", color= "pink3") +
  theme_minimal() +
  labs(title = "Perception of Inclusive Insitutions on Attachment",
       subtitle = "(mean attachment to country - mean attachment to Europe, scale from 1-10)",
       x = "\nInclusivity",
       y = "Mean Difference \n")+
  theme(plot.title = element_text(face= "bold", hjust = 0.5), 
        plot.subtitle = element_text(hjust = 0.5))

# inclusiveness- country

by_inclusivity1 <- svyess|>
  select(psppsgva, atcherp, atchctr)|>
  drop_na()|>
  group_by(psppsgva)|>
  summarize(mean= survey_mean(atchctr))

by_inclusivity1$psppsgva <-
  factor(by_inclusivity1$psppsgva,
         labels = c("Not at all", "Very Little", "Some", "A lot", "A great deal"))

ggplot(by_inclusivity1, aes(x= psppsgva, y=mean)) +
  geom_col(fill = "maroon3", color= "maroon4") +
  theme_minimal() +
  labs(title = "Perception of Inclusive Insitutions on Attachment",
       subtitle = "(mean attachment to country)",
       x = "\nInclusivity",
       y = "Mean Difference \n")+
  theme(plot.title = element_text(face= "bold", hjust = 0.5), 
        plot.subtitle = element_text(hjust = 0.5))

```
There is a negative relationship between how inclusive the institutions are and strength of attachment to their country over Europe, with an outlier of those who feel their government is the most inclusive breaking the pattern. When broken down by country attachment, it is clear that while inclusiveness has a small effect on country attachment (a weak positive relationship), the original relationship is more explained by the change in attachment to Europe.
